---
title: "Journal (reproducible report)"
author: "Khaled Sallam"
date: "2020-11-05"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

**IMPORTANT:** You can delete everything in here and start fresh. You might want to start by not deleting anything above this line until you know what that stuff is doing.

This is an `.Rmd` file. It is plain text with special features. Any time you write just like this, it will be compiled to normal text in the website. If you put a \# in front of your text, it will create a top level-header.

# Into the tidyverse Challenge

Last compiled: `r Sys.Date()`

Notice that whatever you define as a top level header, automatically gets put into the table of contents bar on the left. 

```{r}
## First challenge task

# Data Science at TUHH ------------------------------------------------------
# SALES ANALYSIS ----

# 1.0 Load libraries ----

library(tidyverse)

library(readxl)
options(repos="https://cran.rstudio.com" )

# 2.0 Importing Files ----

bikes_tbl      <- read_excel(path = "00_data/01_bike_sales/01_raw_data/bikes.xlsx")
orderlines_tbl <- read_excel("00_data/01_bike_sales/01_raw_data/orderlines.xlsx")
bikeshops_tbl  <- read_excel("00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")

# 3.0 Examining Data ----

orderlines_tbl
glimpse(orderlines_tbl)

# 4.0 Joining Data ----

bike_orderlines_joined_tbl <- orderlines_tbl %>%
  left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))


# 5.0 Wrangling Data ----

bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  separate(col    = location,
           into   = c("city", "state"),
           sep    = ", ") %>%
  mutate(total.price = price * quantity)


# 6.0 Business Insights ----
# 6.1 Sales by State ----

library(lubridate)

# Step 1 - Manipulate

sales_by_state_tbl <- bike_orderlines_wrangled_tbl %>%
  select(state, total.price) %>%
  group_by(state) %>%
  summarize(sales = sum(total.price)) %>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))
sales_by_state_tbl %>%

# Step 2 - Visualize


  
  # Setup canvas with the columns year (x-axis) and sales (y-axis)
  ggplot(aes(x = state, y = sales)) + 
  
  # Geometries
  geom_col(fill = "#2DC6D6") + # Use geom_col for a bar plot
  geom_label(aes(label = sales_text)) + 
  geom_smooth(method = "lm", se = FALSE) + # Adding a trendline
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + # Adding labels to the bars
  # Formatting
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by state",
    subtitle = "",
    x = "", # Override defaults for x and y
    y = "Revenue"
  )


# 6.2 Sales by Year and State ----

# Step 1 - Manipulate
sales_by_year_state_tbl <- bike_orderlines_wrangled_tbl %>%
  
  # Select columns and add a year
  select(order.date, total.price, state) %>%
  mutate(year = year(order.date)) %>%
  
  # Group by and summarize year and main catgegory
  group_by(year, state) %>%
  summarise(sales = sum(total.price)) %>%
  ungroup() %>%
  
  # Format $ Text
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))

sales_by_year_state_tbl  

# Step 2 - Visualize

sales_by_year_state_tbl %>%
  
  # Set up x, y, fill
  ggplot(aes(x = year, y = sales, fill = state)) +
  
  # Geometries
  geom_col() + # Run up to here to get a stacked bar plot
  
  # Facet
  facet_wrap(~ state) +
  
  # Formatting
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue by year and state",
    subtitle = "Each state has a different trend",
    fill = "State" # Changes the legend name
  )


# 7.0 Writing Files ----

# 7.1 Excel ----
install.packages("writexl")
library("writexl")
# bike_orderlines_wrangled_tbl %>%
#   write_xlsx("00_data/01_bike_sales/02_wrangled_data/bike_orderlines.xlsx")
# 
# # 7.2 CSV ----
# bike_orderlines_wrangled_tbl %>%
#   write_csv("00_data/01_bike_sales/02_wrangled_data/bike_orderlines.csv")

# 7.3 RDS ----
bike_orderlines_wrangled_tbl %>% 
  write_rds("00_data/01_bike_sales/02_wrangled_data/bike_orderlines.rds")

```

#Data Acquistion Challenge

``` {r}
# Challenge 1 - API ----
library(httr)
library(jsonlite)
library(dplyr)
library(RSQLite)
library(dplyr)
library(tibble)
library(rvest)

#Covid-19 Germany statistics

url <-  "https://api.covid19api.com/dayone/country/germany/status/confirmed"
resp <- GET(url)

list <- resp %>%
  .$content %>%
  rawToChar() %>%
  fromJSON() %>%
  head(10)

list

#Challenge 2 - Web Scraping

bike_webscraping <- function(url) {
  
  bike_html <- read_html(url)
  bike_url_tbl  <- bike_html %>%
    html_nodes(css = ".catalog-category-bikes__title-text") %>%
    html_text()%>%
    enframe(name = "No.", value = "Bike.Name")
  bike_database_tbl<-bike_url_tbl%>% 
    mutate(price= bike_html%>%
             html_nodes(css =".catalog-category-bikes__price-title")%>% html_text())
  
}
url= "https://www.rosebikes.de/fahrräder/gravel"
bike_prices<-bike_webscraping(url)
saveRDS(bike_prices,"challenge-data_acquistion.rds")
bike_prices

```

Here's an even lower level header

# My second post (note the order)

Last compiled: `r Sys.Date()`
